---
title-block: false
title: ""
author: "" 
date: ""
format: 
    html:
      self-contained: true
      toc: true
      toc-depth: 3
      theme: cosmo
      code-fold: true
fontfamily: roboto
fontsize: 12pt
geometry: a4paper
---

```{=html}
<!-- Title page for HTML output -->
<div style="text-align: center;">
    <h1 style="font-size: 2em; font-weight: bold;">Gaza NowPop: Population nowcasting for Gaza using telecoms data from Nov 23, 2025</h1>
    <br>

    <p style="font-size: 1.2em; font-weight: bold">Real Good Research Ltd.<br>
    <a href="https://realgoodresearch.com" target="_blank" style="font-size: 1em; font-weight: normal">https://realgoodresearch.com</a></p>

    <p style="font-size: 1.2em">Douglas R. Leasure, PhD<sup>1</sup></p>
   
    <br><br>
</div>
<div style="text-align: left;">

    <p><strong>Publication Date:</strong> 26 November 2025</p>
    
    <p><strong>Classification:</strong> Strictly Confidential<sup>2</sup></p>

    <p><strong>Sensitivity:</strong> Severe Sensitivity</p>

    <p><strong>Suggested Citation:</strong> Leasure DR. 2025. Gaza NowPop: Population nowcasting for Gaza using telecoms data from Nov 23, 2025. Real Good Research Ltd. Published November 26, 2025.</p>

    <br>

    <p style="font-style: italic;">While every effort was given to produce data suitable for operational purposes, the results are provided "as is" without warranty of any kind. In no event shall the authors or copyright holders be liable for any claim, damages or other liability arising from, out of or in connection with the contents of this report, supplementary data, or source code.</p>

    <hr>
    <p style="font-size: 0.8em"><sup>1</sup><em>Director and Research Data Scientist for Real Good Research Ltd.
    <br>Senior Researcher and Data Scientist for the Demographic Science Unit in the Department of Population Health at the University of Oxford. 
    <br>Note: University of Oxford was not involved in this work.</em></p>
    
    <p style="font-size: 0.8em"><sup>2</sup><em>See <a href="https://www.unocha.org/publications/report/occupied-palestinian-territory/information-sharing-protocol-occupied-palestinian-territory-june-2024" target="_blank">UNOCHA (2024) Information Sharing Protocol for the Occupied Palestinian Territory.</a></em></p>    
</div>

<style>
.filename {
  background-color: #f0f0f0;
  padding: 2px 4px;
  border-radius: 4px;
  font-family: monospace;
}
</style>
```


```{r}
#| include: false

options(scipen = 999)

# libraries
library(dplyr)
library(knitr)
library(kableExtra)
library(DT)

#---- USER OPTIONS ----#
pop_date <- as.Date("2025-11-23")
baseline_date <- as.Date("2025-09-29")
lastweek_date <- as.Date("2025-11-16")
#----------------------#

# directories
data_dir <- file.path("wd", "out", "results", pop_date, "supplementary_data")

if (!dir.exists(data_dir)) {
  data_dir <- file.path("..", data_dir)
}

# load data
pop_gov <- read.csv(file.path(
  data_dir,
  paste0("pop_gov_", pop_date, ".csv")
))
pop_mun <- read.csv(file.path(
  data_dir,
  paste0("pop_mun_", pop_date, ".csv")
))
pop_nbr <- read.csv(file.path(
  data_dir,
  paste0("pop_nbr_", pop_date, ".csv")
))

pop_change_gov <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', baseline_date))),
  paste0("pop_change_gov_", pop_date, ".csv")
))
pop_change_mun <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', baseline_date))),
  paste0("pop_change_mun_", pop_date, ".csv")
))
pop_change_nbr <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', baseline_date))),
  paste0("pop_change_nbr_", pop_date, ".csv")
))

pop_change_weekly_gov <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', lastweek_date))),
  paste0("pop_change_gov_", pop_date, ".csv")
))
pop_change_weekly_mun <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', lastweek_date))),
  paste0("pop_change_mun_", pop_date, ".csv")
))
pop_change_weekly_nbr <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', lastweek_date))),
  paste0("pop_change_nbr_", pop_date, ".csv")
))

# functions
print_pop <- function(values, field, dat){
  dat %>%
    filter(!!rlang::sym(field) %in% values) %>%
    pull(population) %>%
    sum() %>%
    round(-3) %>%
    prettyNum(big.mark=",")
}
```


# Summary  
This report provides population estimates for 23 November 2025 that have been produced from counts of active subscribers assigned to geolocated telecommunications towers for two mobile network operators, including over 1.2 million subscribers. Population estimates were produced on a 100-m grid, assuming a total population of 2.1 million people in the Gaza strip, and then aggregated to neighbourhoods, municipalities, and governorates. Population changes were estimated for each area relative to previous population estimates from November 16 and also compared to September 29 which provided a baseline prior to the ceasfire that began on October 10. 

<strong>Populations appear to be continuing to increase since Nov 16 in Gaza and North Gaza governorates (+`r print_pop(values=c("Gaza", "North Gaza"), field="ADM2_EN", dat=pop_change_weekly_gov)` people) while decreasing primarily from Deir al Balah governorate (`r print_pop(values=c("Deir al Balah"), field="ADM2_EN", dat=pop_change_weekly_gov)`)</strong>. On November 23, Gaza and North Gaza governorates were estimated to have `r print_pop(values=c("Gaza", "North Gaza"), field="ADM2_EN", dat=pop_gov)` people, Deir al Balah had `r print_pop(values=c("Deir al Balah"), field="ADM2_EN", dat=pop_gov)`, and Khan Younis and Rafah had `r print_pop(values=c("Khan Younis", "Rafah"), field="ADM2_EN", dat=pop_gov)`. See the full report below for population estimates in all municipalities and neighbourhoods. 

<strong>Gaza municipality increased by `r print_pop(values=c("Gaza"), field="ADM3_EN", dat=pop_change_weekly_mun)` with the biggest increases in the An Naser neighbourhood (+`r print_pop(values=c("An Naser"), field="ADM4_EN", dat=pop_change_weekly_nbr %>% filter(ADM2_EN == "Gaza"))`). It was notable that the Jabalya municipality of North Gaza had significant increases since November 16 (+`r print_pop(values=c("Jabalya"), field="ADM3_EN", dat=pop_change_weekly_mun)`)</strong>.

In Deir al Balah governorate, the largest decreases since November 16 were from the neighbourhoods of Deir al Balah (south) (`r print_pop(values=c("Deir Al Balah (south)"), field="ADM4_EN", dat=pop_change_weekly_nbr)` people) and An Nuseirat (`r print_pop(values=c("An Nuseirat"), field="ADM4_EN", dat=pop_change_weekly_nbr)` people). In Khan Younis governorate, the largest decreases since November 16 were from the neighbourhoods of Al Mawasi (`r print_pop(values=c("Al Mawasi"), field="ADM4_EN", dat=pop_change_weekly_nbr)` people) and Al Jala'a (`r print_pop(values=c("Al Jala'a"), field="ADM4_EN", dat=pop_change_weekly_nbr)` people). 


<p style="font-size: 0.9em; background-color: #f5f5f5; padding: 10px; border-radius: 8px;"><em><strong>Methodology.</strong> The method approximated the coverage area for each telecommunications tower assuming subscribers were assigned to the nearest tower within 2 km. Total population for each 100-m grid cell was extrapolated from subscriber counts by estimating the penetration rate for each mobile network operator. Population estimates were mapped into the locations of buildings and tents after excluding destroyed or severely damaged buildings. Building damage was based on UNOSAT's latest building damage estimates and tents were manually mapped based on satellite imagery from Oct 14. Populations were assumed to be zero for grid cells outside the coverage area of both telecommunications providers, for grid cells with active evacuation orders, and for areas behind the "yellow line" militarised area along the Gaza border. Because evacuation zones may have small populations remaining, we report those populations as "<100" or "<500" (less than 100 or less than 500 people). This methodology cannot produce quantitative measures of accuracy at any spatial scale due to lack of ground-truth validation data, so triangulation with multiple data sources is encouraged.</em></p>

\newpage
# Population estimation for Nov 23
```{r}
#| echo: false
#| label: fig-pop-grid
#| fig-cap: "Population estimates for every 100-m grid cell."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_grid_", pop_date, ".jpg")
))
```

```{r}
#| echo: false
#| label: fig-pop-nbr
#| fig-cap: "Population estimates aggregated to neighborhoods."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_nbr_", pop_date, ".jpg")
))
```


\newpage
## Governorate-level
```{r}
#| echo: false
#| results: asis

pop_gov_table <- pop_gov |>
  arrange(ADM2_PCODE) |>
  select(ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Population = population
  ) |>
  mutate(
    Population = case_when(
      Population > 500 ~ prettyNum(round(Population), big.mark = ","),
      Population >= 100 & Population < 500 ~ "<500",
      Population < 100 ~ "<100"
    )
  )

pop_gov_caption <- paste0(
  "Population estimates for each governorate on ",
  format(pop_date, "%d %B %Y")
)

pop_gov_table |>
  datatable(
    rownames = FALSE,
    caption = pop_gov_caption,
    options = list(
      paging = FALSE,
      searching = FALSE,
      scrollX = FALSE,
      scrollY = FALSE,
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )

```



## Municipality-level
```{r}
#| echo: false
#| results: asis

pop_mun_table <- pop_mun |>
  arrange(ADM2_PCODE, ADM3_PCODE) |>
  select(ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Population = population
  ) |>
  mutate(
    Population = case_when(
      Population > 500 ~ prettyNum(round(Population), big.mark = ","),
      Population >= 100 & Population < 500 ~ "<500",
      Population < 100 ~ "<100"
    )
  )
  
pop_mun_caption <- paste0(
    "Population estimates for each municipality on ",
    format(pop_date, "%d %B %Y")
  )

pop_mun_table |>
  datatable(
    rownames = FALSE,
    caption = pop_mun_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )

```

## Neighbourhood-level
```{r}
#| echo: false
#| results: asis

pop_nbr_table <- pop_nbr |>
  arrange(ADM2_PCODE, ADM3_PCODE, ADM4_PCODE) |>
  select(ADM4_EN, ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Neighbourhood = ADM4_EN,
    Population = population
  ) |>
  mutate(
    Population = case_when(
      Population > 500 ~ prettyNum(round(Population), big.mark = ","),
      Population >= 100 & Population < 500 ~ "<500",
      Population < 100 ~ "<100"
    ),
    Municipality = case_when(
      nchar(Municipality) > 12 ~ paste0(substr(Municipality, 1, 12), "..."),
      TRUE ~ Municipality
    )
  )

pop_nbr_caption <- paste0(
  "Population estimates for each neighbourhood on ",
  format(pop_date, "%d %B %Y")
)

pop_nbr_table |>
  datatable(
    rownames = FALSE,
    caption = pop_nbr_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )

```

# Population change (16 Nov to 23 Nov 2025)
```{r}
#| echo: false
#| label: fig-pop-change-weekly
#| fig-cap: "Change in population for every 100-m grid cell from 16 November to 23 November 2025."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_change_", lastweek_date, "_to_", pop_date, ".jpg")
))
```

## Governorate-level
```{r}
#| echo: false
#| results: asis

pop_change_weekly_gov_table <- pop_change_weekly_gov |>
  arrange(ADM2_PCODE) |>
  select(ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Population_Change = population
  ) |>
  mutate(
    Population_Change = prettyNum(round(Population_Change), big.mark = ",")
  )

pop_change_weekly_gov_caption = paste0(
  "Estimates of population change for each governorate on ",
  format(pop_date, "%d %B %Y"),
  " compared to ",
  format(lastweek_date, "%d %B %Y")
)

pop_change_weekly_gov_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_weekly_gov_caption,
    options = list(
      searching = FALSE,
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = FALSE,
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```

## Municipality-level
```{r}
#| echo: false
#| results: asis

pop_change_weekly_mun_table <- pop_change_weekly_mun |>
  arrange(ADM2_PCODE, ADM3_PCODE) |>
  select(ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Population_Change = population
  ) |>
  mutate(
    Population_Change = prettyNum(round(Population_Change), big.mark = ",")
  )

pop_change_weekly_mun_caption = paste0(
  "Estimates of population change for each municipality on ",
  format(pop_date, "%d %B %Y"),
  " compared to ",
  format(lastweek_date, "%d %B %Y")
)

pop_change_weekly_mun_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_weekly_mun_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```

## Neighbourhood-level
```{r}
#| echo: false
#| results: asis
pop_change_weekly_nbr_table <- pop_change_weekly_nbr |>
  arrange(ADM2_PCODE, ADM3_PCODE, ADM4_PCODE) |>
  select(ADM4_EN, ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Neighbourhood = ADM4_EN,
    Pop_Change = population
  ) |>
  mutate(
    Pop_Change = prettyNum(round(Pop_Change), big.mark = ","),
    Municipality = case_when(
      nchar(Municipality) > 12 ~ paste0(substr(Municipality, 1, 12), "..."),
      TRUE ~ Municipality
    )
  )

pop_change_weekly_nbr_caption = paste0(
  "Estimates of population change for each neighbourhood on ",
  format(pop_date, "%d %B %Y"),
  " compared to ",
  format(lastweek_date, "%d %B %Y")
)

pop_change_weekly_nbr_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_weekly_nbr_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )

```

# Population change (29 Sept to 23 Nov)
```{r}
#| echo: false
#| label: fig-pop-change-baseline
#| fig-cap: "Change in population for every 100-m grid cell from 29 September to 23 November 2025."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_change_", baseline_date, "_to_", pop_date, ".jpg")
))
```


## Governorate-level
```{r}
#| echo: false
#| results: asis

pop_change_gov_table <- pop_change_gov |>
  arrange(ADM2_PCODE) |>
  select(ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Population_Change = population
  ) |>
  mutate(
    Population_Change = prettyNum(round(Population_Change), big.mark = ",")
  )

pop_change_gov_caption = paste0(
  "Estimates of population change for each governorate on ",
  format(pop_date, "%d %B %Y"),
  "compared to",
  format(baseline_date, "%d %B %Y")
)

pop_change_gov_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_gov_caption,
    options = list(
      searching = FALSE,
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = FALSE,
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```

## Municipality-level
```{r}
#| echo: false
#| results: asis

pop_change_mun_table <- pop_change_mun |>
  arrange(ADM2_PCODE, ADM3_PCODE) |>
  select(ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Population_Change = population
  ) |>
  mutate(
    Population_Change = prettyNum(round(Population_Change), big.mark = ",")
  )

pop_change_mun_caption = paste0(
  "Estimates of population change for each municipality on ",
  format(pop_date, "%d %B %Y"),
  "compared to ",
  format(baseline_date, "%d %B %Y")
)

pop_change_mun_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_mun_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```

## Neighbourhood-level
```{r}
#| echo: false
#| results: asis
pop_change_nbr_table <- pop_change_nbr |>
  arrange(ADM2_PCODE, ADM3_PCODE, ADM4_PCODE) |>
  select(ADM4_EN, ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Neighbourhood = ADM4_EN,
    Pop_Change = population
  ) |>
  mutate(
    Pop_Change = prettyNum(round(Pop_Change), big.mark = ","),
    Municipality = case_when(
      nchar(Municipality) > 12 ~ paste0(substr(Municipality, 1, 12), "..."),
      TRUE ~ Municipality
    )
  )

pop_change_nbr_caption = paste0(
  "Estimates of population change for each neighbourhood on ",
  format(pop_date, "%d %B %Y"),
  " compared to ",
  format(baseline_date, "%d %B %Y")
)

pop_change_nbr_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_nbr_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```




# Supplementary Data

The following supplementary data accompany this report and are available upon request to UNOCHA through the Assessment and Information Management (AIM) Working Group:

<br>
1. <span class="filename">pop_grid_[date].tif</span>: 100-m gridded population estimates in geotiff format.  
2. <span class="filename">pop_nbr_[date].csv</span>:  Neighbourhood-level population estimates in csv format.  
3. <span class="filename">pop_mun_[date].csv</span>:  Municipality-level population estimates in csv format.  
4. <span class="filename">pop_gov_[date].csv</span>:  Governorate-level population estimates in csv format.  
5. <span class="filename">pop_nbr_[date].gpkg</span>:  Neighbourhood-level population estimates in geopackage format to include spatial geometries defining neighbourhood boundaries.  
6. <span class="filename">pop_mun_[date].gpkg</span>:  Municipality-level population estimates in geopackage format to include spatial geometries defining municipality boundaries.  
7. <span class="filename">pop_gov_[date].gpkg</span>:  Governorate-level population estimates in geopackage format to include spatial geometries defining governorate boundaries.  

<br>
8. <span class="filename">./pop_change_[from-date]/README.txt</span>:  Definition of the dates used to calculate population change.
9. <span class="filename">./pop_change_[from-date]/pop_grid_change_[date].tif</span>:  100-m gridded estimates of population change in geotiff format.  
10. <span class="filename">./pop_change_[from-date]/pop_change_nbr_[date].csv</span>:  Neighbourhood-level estimates of population change in csv format.  
11. <span class="filename">./pop_change_[from-date]/pop_change_mun_[date].csv</span>:  Municipality-level estimates of population change in csv format.  
12. <span class="filename">./pop_change_[from-date]/pop_change_gov_[date].csv</span>:  Governorate-level estimates of population change in csv format.  
13. <span class="filename">./pop_change_[from-date]/pop_change_nbr_[date].gpkg</span>:  Neighbourhood-level estimates of population change in geopackage format to include spatial geometries defining neighbourhood boundaries.  
14. <span class="filename">./pop_change_[from-date]/pop_change_mun_[date].gpkg</span>:  Municipality-level estimates of population change in geopackage format to include spatial geometries defining municipality boundaries.  
15. <span class="filename">./pop_change_[from-date]/pop_change_gov_[date].gpkg</span>:  Governorate-level estimates of population change in geopackage format to include spatial geometries defining governorate boundaries.  

<br>
16. <span class="filename">fig_pop_grid_[date].jpg</span>:  A map of gridded population estimates (@fig-pop-grid) in JPEG format.  
17. <span class="filename">fig_pop_nbr_[date].jpg</span>:  A map of neighborhood-level population estimates (@fig-pop-nbr) in JPEG format.  
18. <span class="filename">fig_pop_grid_change_[date]_to__[date].jpg</span>:  A map of gridded estimates of population change (@fig-pop-change-weekly, @fig-pop-change-baseline) in JPEG format.  
