---
title-block: false
title: ""
author: "" 
date: ""
format: 
    html:
      self-contained: true
      toc: true
      toc-depth: 3
      theme: cosmo
      code-fold: true
fontfamily: roboto
fontsize: 12pt
geometry: a4paper
---

```{=html}
<!-- Title page for HTML output -->
<div style="text-align: center;">
    <h1 style="font-size: 2em; font-weight: bold;">Gaza NowPop: Population nowcasting for Gaza using telecoms data from Nov 30, 2025</h1>
    <br>

    <p style="font-size: 1.2em; font-weight: bold">Real Good Research Ltd.<br>
    <a href="https://realgoodresearch.com" target="_blank" style="font-size: 1em; font-weight: normal">https://realgoodresearch.com</a></p>

    <p style="font-size: 1.2em">Douglas R. Leasure, PhD<sup>1</sup></p>
   
    <br><br>
</div>
<div style="text-align: left;">

    <p><strong>Publication Date:</strong> 5 December 2025</p>
    
    <p><strong>Classification:</strong> Strictly Confidential<sup>2</sup></p>

    <p><strong>Sensitivity:</strong> Severe Sensitivity</p>

    <p><strong>Suggested Citation:</strong> Leasure DR. 2025. Gaza NowPop: Population nowcasting for Gaza using telecoms data from Nov 30, 2025. Real Good Research Ltd. Published December 5, 2025.</p>

    <br>

    <p style="font-style: italic;">While every effort was given to produce data suitable for operational purposes, the results are provided "as is" without warranty of any kind. In no event shall the authors or copyright holders be liable for any claim, damages or other liability arising from, out of or in connection with the contents of this report, supplementary data, or source code.</p>

    <hr>
    <p style="font-size: 0.8em"><sup>1</sup><em>Director and Research Data Scientist for Real Good Research Ltd.
    <br>Senior Researcher and Data Scientist for the Demographic Science Unit in the Department of Population Health at the University of Oxford. 
    <br>Note: University of Oxford was not involved in this work.</em></p>
    
    <p style="font-size: 0.8em"><sup>2</sup><em>See <a href="https://www.unocha.org/publications/report/occupied-palestinian-territory/information-sharing-protocol-occupied-palestinian-territory-june-2024" target="_blank">UNOCHA (2024) Information Sharing Protocol for the Occupied Palestinian Territory.</a></em></p>    
</div>

<style>
.filename {
  background-color: #f0f0f0;
  padding: 2px 4px;
  border-radius: 4px;
  font-family: monospace;
}
</style>
```


```{r}
#| include: false

options(scipen = 999)

# libraries
library(dplyr)
library(knitr)
library(kableExtra)
library(DT)

#---- USER OPTIONS ----#
pop_date <- as.Date("2025-11-30")
baseline_date <- as.Date("2025-09-29")
lastweek_date <- as.Date("2025-11-23")
#----------------------#

# directories
data_dir <- file.path("wd", "out", "results", pop_date, "supplementary_data")

if (!dir.exists(data_dir)) {
  data_dir <- file.path("..", data_dir)
}

# load data
pop_gov <- read.csv(file.path(
  data_dir,
  paste0("pop_gov_", pop_date, ".csv")
))
pop_mun <- read.csv(file.path(
  data_dir,
  paste0("pop_mun_", pop_date, ".csv")
))
pop_nbr <- read.csv(file.path(
  data_dir,
  paste0("pop_nbr_", pop_date, ".csv")
))

pop_change_gov <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', baseline_date))),
  paste0("pop_change_gov_", pop_date, ".csv")
))
pop_change_mun <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', baseline_date))),
  paste0("pop_change_mun_", pop_date, ".csv")
))
pop_change_nbr <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', baseline_date))),
  paste0("pop_change_nbr_", pop_date, ".csv")
))

pop_change_weekly_gov <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', lastweek_date))),
  paste0("pop_change_gov_", pop_date, ".csv")
))
pop_change_weekly_mun <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', lastweek_date))),
  paste0("pop_change_mun_", pop_date, ".csv")
))
pop_change_weekly_nbr <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', lastweek_date))),
  paste0("pop_change_nbr_", pop_date, ".csv")
))

# functions
print_pop <- function(values, field, dat){
  dat %>%
    filter(!!rlang::sym(field) %in% values) %>%
    pull(population) %>%
    sum() %>%
    round(-3) %>%
    prettyNum(big.mark=",")
}
```


# Summary  
This report provides population estimates for 30 November 2025 that have been produced from counts of active subscribers assigned to geolocated telecommunications towers for two mobile network operators, including over 1.2 million subscribers. Population estimates were produced on a 100-m grid, assuming a total population of 2.1 million people in the Gaza strip, and then aggregated to neighbourhoods, municipalities, and governorates. Population changes were estimated for each area relative to previous population estimates from November 23 and also compared to September 29 which provided a baseline prior to the ceasfire that began on October 10. 

<strong>Populations increases in Gaza and North Gaza governorates have slowed in the period since Nov 23 compared to recent periods (i.e. see previous report for period from Nov 16 to 23), although population estimates have continued to increase for North Gaza governorate (+`r print_pop(values=c("North Gaza"), field="ADM2_EN", dat=pop_change_weekly_gov)` people).</strong> On November 30, Gaza and North Gaza governorates were estimated to have `r print_pop(values=c("Gaza", "North Gaza"), field="ADM2_EN", dat=pop_gov)` people, Deir al Balah had `r print_pop(values=c("Deir al Balah"), field="ADM2_EN", dat=pop_gov)`, and Khan Younis and Rafah had `r print_pop(values=c("Khan Younis", "Rafah"), field="ADM2_EN", dat=pop_gov)`. See the full report below for population estimates in all municipalities and neighbourhoods. The largest population decreases continue to be from Deir al Balah governorate (`r print_pop(values=c("Deir al Balah"), field="ADM2_EN", dat=pop_change_weekly_gov)`).  

<strong>Jabalya municipality increased by `r print_pop(values=c("Jabalya"), field="ADM3_EN", dat=pop_change_weekly_mun)` with the biggest increases in the Al Karameh (+`r print_pop(values=c("Al Karameh"), field="ADM4_EN", dat=pop_change_weekly_nbr)`) and Ibad Ar-Rahman neighbourhoods (+`r print_pop(values=c("Ibad Ar-Rahman"), field="ADM4_EN", dat=pop_change_weekly_nbr)`). </strong>.

In Khan Younis governorate, the largest decreases since November 23 continue to be from the Al Mawasi neighbourhood (`r print_pop(values=c("Al Mawasi"), field="ADM4_EN", dat=pop_change_weekly_nbr)` people) with increases for the Khan Yunis City Centre (+`r print_pop(values=c("City Centre"), field="ADM4_EN", dat=pop_change_weekly_nbr %>% filter(ADM3_EN=="Khan Yunis"))` people) and Al Jala'a (+`r print_pop(values=c("Al Jala'a"), field="ADM4_EN", dat=pop_change_weekly_nbr)` people). In Deir al Balah governorate, the largest decrease since November 23 was from the neighbourhood of Al Amal (`r print_pop(values=c("Al Amal"), field="ADM4_EN", dat=pop_change_weekly_nbr)` people) and the largest increase was for Al Maghazi Camp (+`r print_pop(values=c("Al Maghazi Camp"), field="ADM4_EN", dat=pop_change_weekly_nbr)` people). 

> <strong>Important Note:</strong> Review of recent satellite imagery from Dec 1, 2025 indicated signficant changes in the geographic distribution of tents, with more tents seen in the north and near the "yellow line". Our gridded population estimates are dependent on an up-to-date tent mapping layer which is not currently available. For this reason, we have omitted 100-m gridded population estimates from this data release. The neighbourhood-level population estimates are less sensitive to this issue. It is strongly recommended to initiate an effort to automate the mapping of tents from satellite imagery. We have identified a partner with a prototype machine learning algorithm for this purpose and secured access to regularly updated satellite imagery. This is a top priority for next steps.

<p style="font-size: 0.9em; background-color: #f5f5f5; padding: 10px; border-radius: 8px;"><em><strong>Methodology.</strong> The method approximated the coverage area for each telecommunications tower assuming subscribers were assigned to the nearest tower within 2 km. Total population for each 100-m grid cell was extrapolated from subscriber counts by estimating the penetration rate for each mobile network operator. Population estimates were mapped into the locations of buildings and tents after excluding destroyed or severely damaged buildings. Building damage was based on UNOSAT's latest building damage estimates and tents were manually mapped based on satellite imagery from Oct 14. Populations were assumed to be zero for grid cells outside the coverage area of both telecommunications providers, for grid cells with active evacuation orders, and for areas behind the "yellow line" militarised area along the Gaza border. Because evacuation zones may have small populations remaining, we report those populations as "<100" or "<500" (less than 100 or less than 500 people). This methodology cannot produce quantitative measures of accuracy at any spatial scale due to lack of ground-truth validation data, so triangulation with multiple data sources is encouraged.</em></p>


\newpage
# Population estimation for Nov 30
<!-- ```{r}
#| echo: false
#| label: fig-pop-grid
#| fig-cap: "Population estimates for every 100-m grid cell."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_grid_", pop_date, ".jpg")
))
``` -->

```{r}
#| echo: false
#| label: fig-pop-nbr
#| fig-cap: "Population estimates aggregated to neighborhoods."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_nbr_", pop_date, ".jpg")
))
```


\newpage
## Governorate-level
```{r}
#| echo: false
#| results: asis

pop_gov_table <- pop_gov |>
  arrange(ADM2_PCODE) |>
  select(ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Population = population
  ) |>
  mutate(
    Population = case_when(
      Population > 500 ~ prettyNum(round(Population), big.mark = ","),
      Population >= 100 & Population < 500 ~ "<500",
      Population < 100 ~ "<100"
    )
  )

pop_gov_caption <- paste0(
  "Population estimates for each governorate on ",
  format(pop_date, "%d %B %Y")
)

pop_gov_table |>
  datatable(
    rownames = FALSE,
    caption = pop_gov_caption,
    options = list(
      paging = FALSE,
      searching = FALSE,
      scrollX = FALSE,
      scrollY = FALSE,
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )

```



## Municipality-level
```{r}
#| echo: false
#| results: asis

pop_mun_table <- pop_mun |>
  arrange(ADM2_PCODE, ADM3_PCODE) |>
  select(ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Population = population
  ) |>
  mutate(
    Population = case_when(
      Population > 500 ~ prettyNum(round(Population), big.mark = ","),
      Population >= 100 & Population < 500 ~ "<500",
      Population < 100 ~ "<100"
    )
  )
  
pop_mun_caption <- paste0(
    "Population estimates for each municipality on ",
    format(pop_date, "%d %B %Y")
  )

pop_mun_table |>
  datatable(
    rownames = FALSE,
    caption = pop_mun_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )

```

## Neighbourhood-level
```{r}
#| echo: false
#| results: asis

pop_nbr_table <- pop_nbr |>
  arrange(ADM2_PCODE, ADM3_PCODE, ADM4_PCODE) |>
  select(ADM4_EN, ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Neighbourhood = ADM4_EN,
    Population = population
  ) |>
  mutate(
    Population = case_when(
      Population > 500 ~ prettyNum(round(Population), big.mark = ","),
      Population >= 100 & Population < 500 ~ "<500",
      Population < 100 ~ "<100"
    ),
    Municipality = case_when(
      nchar(Municipality) > 12 ~ paste0(substr(Municipality, 1, 12), "..."),
      TRUE ~ Municipality
    )
  )

pop_nbr_caption <- paste0(
  "Population estimates for each neighbourhood on ",
  format(pop_date, "%d %B %Y")
)

pop_nbr_table |>
  datatable(
    rownames = FALSE,
    caption = pop_nbr_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )

```

# Population change (23 Nov to 30 Nov 2025)
```{r}
#| echo: false
#| label: fig-pop-change-weekly
#| fig-cap: "Change in population for every 100-m grid cell from 23 November to 30 November 2025."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_change_", lastweek_date, "_to_", pop_date, ".jpg")
))
```

## Governorate-level
```{r}
#| echo: false
#| results: asis

pop_change_weekly_gov_table <- pop_change_weekly_gov |>
  arrange(ADM2_PCODE) |>
  select(ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Population_Change = population
  ) |>
  mutate(
    Population_Change = prettyNum(round(Population_Change), big.mark = ",")
  )

pop_change_weekly_gov_caption = paste0(
  "Estimates of population change for each governorate on ",
  format(pop_date, "%d %B %Y"),
  " compared to ",
  format(lastweek_date, "%d %B %Y")
)

pop_change_weekly_gov_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_weekly_gov_caption,
    options = list(
      searching = FALSE,
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = FALSE,
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```

## Municipality-level
```{r}
#| echo: false
#| results: asis

pop_change_weekly_mun_table <- pop_change_weekly_mun |>
  arrange(ADM2_PCODE, ADM3_PCODE) |>
  select(ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Population_Change = population
  ) |>
  mutate(
    Population_Change = prettyNum(round(Population_Change), big.mark = ",")
  )

pop_change_weekly_mun_caption = paste0(
  "Estimates of population change for each municipality on ",
  format(pop_date, "%d %B %Y"),
  " compared to ",
  format(lastweek_date, "%d %B %Y")
)

pop_change_weekly_mun_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_weekly_mun_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```

## Neighbourhood-level
```{r}
#| echo: false
#| results: asis
pop_change_weekly_nbr_table <- pop_change_weekly_nbr |>
  arrange(ADM2_PCODE, ADM3_PCODE, ADM4_PCODE) |>
  select(ADM4_EN, ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Neighbourhood = ADM4_EN,
    Pop_Change = population
  ) |>
  mutate(
    Pop_Change = prettyNum(round(Pop_Change), big.mark = ","),
    Municipality = case_when(
      nchar(Municipality) > 12 ~ paste0(substr(Municipality, 1, 12), "..."),
      TRUE ~ Municipality
    )
  )

pop_change_weekly_nbr_caption = paste0(
  "Estimates of population change for each neighbourhood on ",
  format(pop_date, "%d %B %Y"),
  " compared to ",
  format(lastweek_date, "%d %B %Y")
)

pop_change_weekly_nbr_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_weekly_nbr_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )

```

# Population change (29 Sept to 30 Nov)
```{r}
#| echo: false
#| label: fig-pop-change-baseline
#| fig-cap: "Change in population for every 100-m grid cell from 29 September to 30 November 2025."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_change_", baseline_date, "_to_", pop_date, ".jpg")
))
```


## Governorate-level
```{r}
#| echo: false
#| results: asis

pop_change_gov_table <- pop_change_gov |>
  arrange(ADM2_PCODE) |>
  select(ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Population_Change = population
  ) |>
  mutate(
    Population_Change = prettyNum(round(Population_Change), big.mark = ",")
  )

pop_change_gov_caption = paste0(
  "Estimates of population change for each governorate on ",
  format(pop_date, "%d %B %Y"),
  "compared to",
  format(baseline_date, "%d %B %Y")
)

pop_change_gov_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_gov_caption,
    options = list(
      searching = FALSE,
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = FALSE,
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```

## Municipality-level
```{r}
#| echo: false
#| results: asis

pop_change_mun_table <- pop_change_mun |>
  arrange(ADM2_PCODE, ADM3_PCODE) |>
  select(ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Population_Change = population
  ) |>
  mutate(
    Population_Change = prettyNum(round(Population_Change), big.mark = ",")
  )

pop_change_mun_caption = paste0(
  "Estimates of population change for each municipality on ",
  format(pop_date, "%d %B %Y"),
  "compared to ",
  format(baseline_date, "%d %B %Y")
)

pop_change_mun_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_mun_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```

## Neighbourhood-level
```{r}
#| echo: false
#| results: asis
pop_change_nbr_table <- pop_change_nbr |>
  arrange(ADM2_PCODE, ADM3_PCODE, ADM4_PCODE) |>
  select(ADM4_EN, ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Neighbourhood = ADM4_EN,
    Pop_Change = population
  ) |>
  mutate(
    Pop_Change = prettyNum(round(Pop_Change), big.mark = ","),
    Municipality = case_when(
      nchar(Municipality) > 12 ~ paste0(substr(Municipality, 1, 12), "..."),
      TRUE ~ Municipality
    )
  )

pop_change_nbr_caption = paste0(
  "Estimates of population change for each neighbourhood on ",
  format(pop_date, "%d %B %Y"),
  " compared to ",
  format(baseline_date, "%d %B %Y")
)

pop_change_nbr_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_nbr_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```




# Supplementary Data

The following supplementary data accompany this report and are available upon request to UNOCHA through the Assessment and Information Management (AIM) Working Group:

<br>
1. <span class="filename">pop_nbr_[date].csv</span>:  Neighbourhood-level population estimates in csv format.  
2. <span class="filename">pop_mun_[date].csv</span>:  Municipality-level population estimates in csv format.  
3. <span class="filename">pop_gov_[date].csv</span>:  Governorate-level population estimates in csv format.  
4. <span class="filename">pop_nbr_[date].gpkg</span>:  Neighbourhood-level population estimates in geopackage format to include spatial geometries defining neighbourhood boundaries.  
5. <span class="filename">pop_mun_[date].gpkg</span>:  Municipality-level population estimates in geopackage format to include spatial geometries defining municipality boundaries.  
6. <span class="filename">pop_gov_[date].gpkg</span>:  Governorate-level population estimates in geopackage format to include spatial geometries defining governorate boundaries.  

<br>
7. <span class="filename">./pop_change_[from-date]/README.txt</span>:  Definition of the dates used to calculate population change.
8. <span class="filename">./pop_change_[from-date]/pop_change_nbr_[date].csv</span>:  Neighbourhood-level estimates of population change in csv format.  
9. <span class="filename">./pop_change_[from-date]/pop_change_mun_[date].csv</span>:  Municipality-level estimates of population change in csv format.  
10. <span class="filename">./pop_change_[from-date]/pop_change_gov_[date].csv</span>:  Governorate-level estimates of population change in csv format.  
11. <span class="filename">./pop_change_[from-date]/pop_change_nbr_[date].gpkg</span>:  Neighbourhood-level estimates of population change in geopackage format to include spatial geometries defining neighbourhood boundaries.  
12. <span class="filename">./pop_change_[from-date]/pop_change_mun_[date].gpkg</span>:  Municipality-level estimates of population change in geopackage format to include spatial geometries defining municipality boundaries.  
13. <span class="filename">./pop_change_[from-date]/pop_change_gov_[date].gpkg</span>:  Governorate-level estimates of population change in geopackage format to include spatial geometries defining governorate boundaries.  

<br>
14. <span class="filename">fig_pop_nbr_[date].jpg</span>:  A map of neighborhood-level population estimates (@fig-pop-nbr) in JPEG format.  
15. <span class="filename">fig_pop_grid_change_[date]_to__[date].jpg</span>:  A map of neighbourhood level estimates of population change (@fig-pop-change-weekly, @fig-pop-change-baseline) in JPEG format.  
