---
title: "Population nowcasting for the Gaza Strip using telecommunications data from October 26, 2025"
author: Douglas R. Leasure\footnote{Director and Research Data Scientist at Real Good Research Ltd. (https://realgoodresearch.com), and Senior Researcher at the Demographic Science Unit, Nuffield Department of Population Health, University of Oxford.}
date: "30 October 2025"
format: 
    pdf:
        number-sections: false
        toc: false
        toc-depth: 3
        latex-engine: xelatex
fontfamily: roboto
fontsize: 12pt
geometry: a4paper
output: pdf_document
---

**Classification:** Strictly Confidential\footnote{See UNOCHA (2024) Information Sharing Protocol for the Occupied Palestinian Territory, available from https://www.unocha.org/publications/report/occupied-palestinian-territory/information-sharing-protocol-occupied-palestinian-territory-june-2024}  

**Sensitivity:** Severe Sensitivity  

**Suggested Citation:** Leasure DR. 2025. Gridded population nowcasting for the Gaza Strip using telecommunications data from Oct 26, 2025. Published October 30, 2025.

\vfill
*While every effort was given to produce data suitable for operational purposes, the results are provided "as is" without warranty of any kind. In no event shall the authors or copyright holders be liable for any claim, damages or other liability arising from, out of or in connection with the contents of this report, supplementary data, or source code.*

\newpage

\hypersetup{linkcolor=black}
<!-- \setcounter{tocdepth}{3}
\tableofcontents -->


```{r}
#| include: false

options(scipen = 999)

# libraries
library(dplyr)
library(knitr)
library(kableExtra)

#---- USER OPTIONS ----#
pop_date <- as.Date("2025-10-26")
#----------------------#

# directories
data_dir <- file.path("wd", "out", "results", pop_date, "supplementary_data")

if (!dir.exists(data_dir)) {
  data_dir <- file.path("..", data_dir)
}

# load data
pop_gov <- read.csv(file.path(
  data_dir,
  paste0("pop_gov_", pop_date, ".csv")
))
pop_mun <- read.csv(file.path(
  data_dir,
  paste0("pop_mun_", pop_date, ".csv")
))
pop_nbr <- read.csv(file.path(
  data_dir,
  paste0("pop_nbr_", pop_date, ".csv")
))

pop_change_gov <- read.csv(file.path(
  file.path(data_dir, "pop_change"),
  paste0("pop_change_gov_", pop_date, ".csv")
))
pop_change_mun <- read.csv(file.path(
  file.path(data_dir, "pop_change"),
  paste0("pop_change_mun_", pop_date, ".csv")
))
pop_change_nbr <- read.csv(file.path(
  file.path(data_dir, "pop_change"),
  paste0("pop_change_nbr_", pop_date, ".csv")
))
```


\newpage

# Summary  

This report provides population estimates for 26 October 2025 that have been produced from counts of active subscribers assigned to geolocated telecommunications towers for two mobile network operators, including over 1.2 million subscribers. Population estimates were produced on a 100-m grid, assuming a total population of 2.1 million people in the Gaza strip, and then aggregated to neighbourhoods, municipalities, and governorates. Population changes were estimated for each area relative to our previous population estimates from 29 September 2025 which provided a baseline prior to the ceasfire that began on 10 October 2025. 

Gaza and North Gaza governorates were estimated to have `r pop_gov %>% filter(ADM2_PCODE %in% c(255,260)) %>% pull(population) %>% sum() %>% round() %>% prettyNum(big.mark=",")` people, Deir al Balah had `r pop_gov %>% filter(ADM2_PCODE==265) %>% pull(population) %>% round() %>% prettyNum(big.mark=",")`, and Khan Younis and Rafah had `r pop_gov %>% filter(ADM2_PCODE %in% c(270,275)) %>% pull(population) %>% sum() %>% round() %>% prettyNum(big.mark=",")`. See the report below for population estimates in municipalities and neighbourhoods.

Estimates of population change since September 29 indicated that the population of Deir al Balah governorate decreased by `r pop_change_gov %>% filter(ADM2_PCODE==265) %>% pull(population) %>% round() %>% prettyNum(big.mark=",")` and the population of Khan Younis governorate decreased by `r pop_change_gov %>% filter(ADM2_PCODE==270) %>% pull(population) %>% round() %>% prettyNum(big.mark=",")` people. In Deir al Balah governorate, the largest decreases were from the neighbourhoods of An Nuseirat (`r pop_change_nbr %>% filter(ADM4_PCODE==26501147) %>% pull(population) %>% round() %>% prettyNum(big.mark=",")`), Deir al Balah (south) (`r pop_change_nbr %>% filter(ADM4_PCODE==26510152) %>% pull(population) %>% round() %>% prettyNum(big.mark=",")`), and As Sahabah (`r pop_change_nbr %>% filter(ADM4_PCODE==2650577) %>% pull(population) %>% round() %>% prettyNum(big.mark=",")`). In Khan Younis governorate, the Al Mawasi neighbourhood decreased by `r pop_change_nbr %>% filter(ADM4_PCODE==27002154) %>% pull(population) %>% round() %>% prettyNum(big.mark=",")` people while Khan Younis Camp increased by `r pop_change_nbr %>% filter(ADM4_PCODE==27003176) %>% pull(population) %>% round() %>% prettyNum(big.mark=",")`. 

The northern governorates of Gaza and North Gaza increased by `r pop_change_gov %>% filter(ADM2_PCODE %in% c(255,260)) %>% pull(population) %>% sum() %>% round() %>% prettyNum(big.mark=",")` people over this time period. Gaza municipality increased by `r pop_change_mun %>% filter(ADM3_PCODE == 26001) %>% pull(population) %>% round() %>% prettyNum(big.mark=",")` with most of that increase in the neighbourhoods of Northern Remel (`r pop_change_nbr %>% filter(ADM4_PCODE==2600118) %>% pull(population) %>% round() %>% prettyNum(big.mark=",")`), Southern Remel (`r pop_change_nbr %>% filter(ADM4_PCODE==2600119) %>% pull(population) %>% round() %>% prettyNum(big.mark=",")`), and An Naser (`r pop_change_nbr %>% filter(ADM4_PCODE==2600123) %>% pull(population) %>% round() %>% prettyNum(big.mark=",")`).

*Methodology.* The method approximated the coverage area for each telecommunications tower assuming subscribers were assigned to the nearest tower within 2 km. Total population for each 100-m grid cell was extrapolated from subscriber counts by estimating the penetration rate for each mobile network operator. Population estimates were mapped into the locations of buildings, so populations living in tents may be incorrectly mapped into grid cells with buildings because systematic tent mapping data is currently unavailable. Populations were assumed to be zero for grid cells outside the coverage area of both telecommunications providers, for grid cells with active evacuation orders, and for areas behind the "yellow line" militarised area along the Gaza border. Because evacuation zones may have small populations remaining, we report those populations as "<100" or "<500" (less than 100 or less than 500 people). This methodology cannot produce quantitative measures of accuracy at any spatial scale due to lack of ground-truth validation data, so triangulation with multiple data sources is encouraged.  

\newpage
# Population estimation
```{r}
#| echo: false
#| label: fig-pop-grid
#| fig-cap: "Population estimates for every 100-m grid cell."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_grid_", pop_date, ".jpg")
))
```

```{r}
#| echo: false
#| label: fig-pop-nbr
#| fig-cap: "Gridded population estimates aggregated to neighborhoods."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_nbr_", pop_date, ".jpg")
))
```


\newpage
## Governorate-level
```{r}
#| echo: false
#| results: asis

pop_gov |>
  arrange(ADM2_PCODE) |>
  select(ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Population = population
  ) |>
  mutate(
    Population = case_when(
      Population > 500 ~ prettyNum(round(Population), big.mark = ","),
      Population >= 100 & Population < 500 ~ "<500",
      Population < 100 ~ "<100"
    )
  ) |>
  kable(
    caption = paste0(
      "Population estimates for each governorate on ",
      format(pop_date, "%d %B %Y"),
      ". {#tbl-pop-gov}"
    ),
    booktabs = TRUE
  )
```

## Municipality-level
```{r}
#| echo: false
#| results: asis

pop_mun |>
  arrange(ADM2_PCODE, ADM3_PCODE) |>
  select(ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Population = population
  ) |>
  mutate(
    Population = case_when(
      Population > 500 ~ prettyNum(round(Population), big.mark = ","),
      Population >= 100 & Population < 500 ~ "<500",
      Population < 100 ~ "<100"
    )
  ) |>
  kable(
    caption = paste0(
      "Population estimates for each municipality on ",
      format(pop_date, "%d %B %Y"),
      ". {label: tbl-pop-mun}"
    ),
    booktabs = TRUE
  )
```

## Neighbourhood-level
```{r}
#| echo: false
#| results: asis

pop_nbr |>
  arrange(ADM2_PCODE, ADM3_PCODE, ADM4_PCODE) |>
  select(ADM4_EN, ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Neighbourhood = ADM4_EN,
    Population = population
  ) |>
  mutate(
    Population = case_when(
      Population > 500 ~ prettyNum(round(Population), big.mark = ","),
      Population >= 100 & Population < 500 ~ "<500",
      Population < 100 ~ "<100"
    ),
    Municipality = case_when(
      nchar(Municipality) > 12 ~ paste0(substr(Municipality, 1, 12), "..."),
      TRUE ~ Municipality
    )
  ) |>
  kable(
    caption = paste0(
      "Population estimates for each neighbourhood on ",
      format(pop_date, "%d %B %Y"),
      ". {label: tbl-pop-nbr}"
    ),
    booktabs = TRUE
  )
```

\newpage 
# Population change (29 September to 26 October 2025)
```{r}
#| echo: false
#| label: fig-pop-change
#| fig-cap: "Change in population for every 100-m grid cell from 29 September to 26 October 2025."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_change_", pop_date, ".jpg")
))
```

\newpage
## Governorate-level
```{r}
#| echo: false
#| results: asis

pop_change_gov |>
  arrange(ADM2_PCODE) |>
  select(ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Population_Change = population
  ) |>
  mutate(
    Population_Change = prettyNum(round(Population_Change), big.mark = ",")
  ) |>
  kable(
    caption = paste0(
      "Estimates of population change for each governorate on ",
      format(pop_date, "%d %B %Y"),
      ". {#tbl-pop-change-gov}"
    ),
    booktabs = TRUE
  )
```

## Municipality-level
```{r}
#| echo: false
#| results: asis

pop_change_mun |>
  arrange(ADM2_PCODE, ADM3_PCODE) |>
  select(ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Population_Change = population
  ) |>
  mutate(
    Population_Change = prettyNum(round(Population_Change), big.mark = ",")
  ) |>
  kable(
    caption = paste0(
      "Estimates of population change for each municipality on ",
      format(pop_date, "%d %B %Y"),
      ". {label: tbl-pop-mun}"
    ),
    booktabs = TRUE
  )
```

## Neighbourhood-level
```{r}
#| echo: false
#| results: asis

pop_change_nbr |>
  arrange(ADM2_PCODE, ADM3_PCODE, ADM4_PCODE) |>
  select(ADM4_EN, ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Neighbourhood = ADM4_EN,
    Pop_Change = population
  ) |>
  mutate(
    Pop_Change = prettyNum(round(Pop_Change), big.mark = ","),
    Municipality = case_when(
      nchar(Municipality) > 12 ~ paste0(substr(Municipality, 1, 12), "..."),
      TRUE ~ Municipality
    )
  ) |>
  kable(
    caption = paste0(
      "Estimates of population change for each neighbourhood on ",
      format(pop_date, "%d %B %Y"),
      ". {label: tbl-pop-nbr}"
    ),
    booktabs = TRUE
  )
```


\newpage
# Supplementary Data

The following supplementary data accompany this report and are available upon request to UNOCHA through the Assessment and Information Management (AIM) Working Group:  

1. pop_grid_[date].tif - 100-m gridded population estimates in geotiff format.  
2. pop_nbr_[date].csv - Neighbourhood-level population estimates in csv format.  
3. pop_mun_[date].csv - Municipality-level population estimates in csv format.  
4. pop_gov_[date].csv - Governorate-level population estimates in csv format.  
5. pop_nbr_[date].gpkg - Neighbourhood-level population estimates in geopackage format to include spatial geometries defining neighbourhood boundaries.  
6. pop_mun_[date].gpkg - Municipality-level population estimates in geopackage format to include spatial geometries defining municipality boundaries.  
7. pop_gov_[date].gpkg - Governorate-level population estimates in geopackage format to include spatial geometries defining governorate boundaries.  


8. ./pop_change/README.txt - Definition of the dates used to calculate population change.
9. ./pop_change/pop_grid_change_[date].tif - 100-m gridded estimates of population change in geotiff format.  
10. ./pop_change/pop_change_nbr_[date].csv - Neighbourhood-level estimates of population change in csv format.  
11. ./pop_change/pop_change_mun_[date].csv - Municipality-level estimates of population change in csv format.  
12. ./pop_change/pop_change_gov_[date].csv - Governorate-level estimates of population change in csv format.  
13. ./pop_change/pop_change_nbr_[date].gpkg - Neighbourhood-level estimates of population change in geopackage format to include spatial geometries defining neighbourhood boundaries.  
14. ./pop_change/pop_change_mun_[date].gpkg - Municipality-level estimates of population change in geopackage format to include spatial geometries defining municipality boundaries.  
15. ./pop_change/pop_change_gov_[date].gpkg - Governorate-level estimates of population change in geopackage format to include spatial geometries defining governorate boundaries.  


16. fig_pop_grid_[date].jpg - A map of gridded population estimates (@fig-pop-grid) in JPEG format.  
17. fig_pop_nbr_[date].jpg - A map of neighborhood-level population estimates (@fig-pop-nbr) in JPEG format.  
18. fig_pop_grid_change_[date].jpg - A map of gridded estimates of population change (@fig-pop-nbr) in JPEG format.  
