---
title-block: false
title: ""
author: "" 
date: ""
format: 
    html:
      self-contained: true
      toc: true
      toc-depth: 3
      theme: cosmo
      code-fold: true
fontfamily: roboto
fontsize: 12pt
geometry: a4paper
---

```{=html}
<!-- Title page for HTML output -->
<div style="text-align: center;">
    <h1 style="font-size: 2em; font-weight: bold;">Gaza NowPop: Population nowcasting for Gaza using telecoms data from Jan 25, 2026</h1>
    <br>

    <p style="font-size: 1.2em; font-weight: bold">Real Good Research Ltd.<br>
    <a href="https://realgoodresearch.com" target="_blank" style="font-size: 1em; font-weight: normal">https://realgoodresearch.com</a></p>

    <p style="font-size: 1.2em">Douglas R. Leasure, PhD<sup>1</sup></p>
   
    <br><br>
</div>
<div style="text-align: left;">

    <p><strong>Publication Date:</strong> 1 February 2026</p>
    
    <p><strong>Classification:</strong> Restricted<sup>2</sup></p>

    <p><strong>Sensitivity:</strong> Moderate Sensitivity</p>

    <p><strong>Suggested Citation:</strong> Leasure DR. 2025. Gaza NowPop: Population nowcasting for Gaza using telecoms data from Jan 25, 2026. Real Good Research Ltd. Published February 1, 2026.</p>

    <br>

    <p style="font-style: italic; font-size: 0.8em">While every effort was given to produce data suitable for operational purposes, the results are provided "as is" without warranty of any kind. In no event shall the authors or copyright holders be liable for any claim, damages or other liability arising from, out of or in connection with the contents of this report, supplementary data, or source code.</p>

    <hr>
    <p style="font-size: 0.8em"><sup>1</sup><em>Director and Research Data Scientist for Real Good Research Ltd.
    <br>Senior Researcher and Data Scientist for the Demographic Science Unit in the Department of Population Health at the University of Oxford. 
    <br>Note: University of Oxford was not involved in this work.</em></p>
    
    <p style="font-size: 0.8em"><sup>2</sup><em>See <a href="https://reliefweb.int/report/occupied-palestinian-territory/information-sharing-protocol-occupied-palestinian-territory-april-2025" target="_blank">UNOCHA (2025) Information Sharing Protocol for the Occupied Palestinian Territory.</a></em></p>    
</div>

<style>
.filename {
  background-color: #f0f0f0;
  padding: 2px 4px;
  border-radius: 4px;
  font-family: monospace;
}
</style>
```


```{r}
#| include: false

options(scipen = 999)

# libraries
library(dplyr)
library(knitr)
library(kableExtra)
library(DT)

#---- USER OPTIONS ----#
pop_date <- as.Date("2026-01-25")
baseline_date <- as.Date("2025-09-29")
lastweek_date <- as.Date("2025-12-16")
#----------------------#

# directories
data_dir <- file.path("wd", "out", "results", pop_date, "supplementary_data")

if (!dir.exists(data_dir)) {
  data_dir <- file.path("..", data_dir)
}

# load data
pop_gov <- read.csv(file.path(
  data_dir,
  paste0("pop_gov_", pop_date, ".csv")
))
pop_mun <- read.csv(file.path(
  data_dir,
  paste0("pop_mun_", pop_date, ".csv")
))
pop_nbr <- read.csv(file.path(
  data_dir,
  paste0("pop_nbr_", pop_date, ".csv")
))

pop_change_gov <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', baseline_date))),
  paste0("pop_change_gov_", pop_date, ".csv")
))
pop_change_mun <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', baseline_date))),
  paste0("pop_change_mun_", pop_date, ".csv")
))
pop_change_nbr <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', baseline_date))),
  paste0("pop_change_nbr_", pop_date, ".csv")
))

pop_change_weekly_gov <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', lastweek_date))),
  paste0("pop_change_gov_", pop_date, ".csv")
))
pop_change_weekly_mun <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', lastweek_date))),
  paste0("pop_change_mun_", pop_date, ".csv")
))
pop_change_weekly_nbr <- read.csv(file.path(
  file.path(data_dir, paste0("pop_change_", gsub('-', '', lastweek_date))),
  paste0("pop_change_nbr_", pop_date, ".csv")
))

# functions
print_pop <- function(values, field, dat) {
  dat %>%
    filter(!!rlang::sym(field) %in% values) %>%
    pull(population) %>%
    sum() %>%
    round(-3) %>%
    prettyNum(big.mark = ",")
}
```


# Summary  
This report provides population estimates for 25 January 2026 that have been produced from counts of active subscribers assigned to geolocated telecommunications towers for two mobile network operators, including over 1.2 million subscribers. The analysis for this reporting period benefitted from up-to-date tent mapping products from UNOSAT that enabled better population estimates with fine spatial granularity and data-driven estimation approaches for areas without mobile network coverage. Population estimates were produced on a 100-m grid, assuming a total population of 2.1 million people in the Gaza strip, and then aggregated to neighbourhoods, municipalities, and governorates. Population changes were estimated for each area relative to previous population estimates from 16 December 2025 and also compared to 29 September 2025 which provided a baseline prior to the ceasefire that began on 10 October 2025. 

<strong>Noteworthy changes in population distribution for this reporting period:  </strong>

1. Continued decreases in the population of Deir al Balah governorate with corresponding increases primarily in Kahn Younis and North Gaza governorates,  
2. Increasing populations in the southern portion of Gaza muncipality with poor mobile network coverage where tent encampments have grown, and  
3. Return of people to the west side of Gaza municipality after heavy rains displaced them in December. 

On 25 January 2026, Gaza and North Gaza governorates were estimated to have 
`r print_pop(values=c("Gaza", "North Gaza"), field="ADM2_EN", dat=pop_gov)` 
people, Deir al Balah had 
`r print_pop(values=c("Deir al Balah"), field="ADM2_EN", dat=pop_gov)`, and Khan Younis and Rafah had 
`r print_pop(values=c("Khan Younis", "Rafah"), field="ADM2_EN", dat=pop_gov)`. 
See the full report below for population estimates in all municipalities and neighbourhoods.  

<strong>Gaza and North Gaza Governorates.</strong> 
There were significant increases in the North Gaza municipalities of 
Jabalya (+`r print_pop(values=c("Jabalya"), field="ADM3_EN", dat=pop_change_weekly_mun)`) and 
Beit Lahiya (+`r print_pop(values=c("Beit Lahiya"), field="ADM3_EN", dat=pop_change_weekly_mun)`). 
Populations in the Gaza neighborhoods of 
Northern Remal (+`r print_pop(values=c("Northern Remal"), field="ADM4_EN", dat=pop_change_weekly_nbr)`) and 
Southern Remal (+`r print_pop(values=c("Southern Remal"), field="ADM4_EN", dat=pop_change_weekly_nbr)`) 
both appeared to have rebounded, although not completely, since declining following the rains in mid-December. 
The Gaza neighborhood of 
Ash Sheikh Radwan (+`r print_pop(values=c("Ash Sheikh Radwan"), field="ADM4_EN", dat=pop_change_weekly_nbr)`) had the largest increase in Gaza governorate during this reporting period. 

<strong>Deir al Balah Governorate.</strong> The population of Deir al Balah continued to decrease since 16 December 2025 
(`r print_pop(values=c("Deir al Balah"), field="ADM2_EN", dat=pop_change_weekly_gov)` people), primarily from the municipalities of 
Deir al Balah (`r print_pop(values=c("Deir al Balah"), field="ADM3_EN", dat=pop_change_weekly_mun)`) and  
An Nuseirat (`r print_pop(values=c("An Nuseirat"), field="ADM3_EN", dat=pop_change_weekly_mun)`). The populations of North Gaza and Khan Younis had corresponding increases over this reporting period
(+`r print_pop(values=c("North Gaza"), field="ADM2_EN", dat=pop_change_weekly_gov)` and 
+`r print_pop(values=c("Khan Younis"), field="ADM2_EN", dat=pop_change_weekly_gov)` people, respectively). 

<strong>Khan Younis Governorate.</strong> Populations increased in the  
An Naser neighbourhood (+`r print_pop(values=c("An Naser"), field="ADM4_EN", dat=pop_change_weekly_nbr)`) while decreasing in 
At Tahrir (`r print_pop(values=c("At Tahrir"), field="ADM4_EN", dat=pop_change_weekly_nbr)`) and 
Al Mawasi (`r print_pop(values=c("Al Mawasi"), field="ADM4_EN", dat=pop_change_weekly_nbr)`).

> <strong>Note:</strong> Before calculating population change relative to our last reporting period (16 December 2025), we revised our population estimates for that date by integrating a UNOSAT tent mapping product representing 12 December 2025 that was unavailable at the time of our last report. Our current estimates of population change therefore were not derived directly from the population figures in our previous report published on 19 December 2025.

<p style="font-size: 0.9em; background-color: #f5f5f5; padding: 10px; border-radius: 8px;"><em><strong>Methodology.</strong> The method approximated the coverage area for each telecommunications tower assuming subscribers were assigned to the nearest tower within 2 km. Total population for each 100-m grid cell was extrapolated from subscriber counts by estimating the penetration rate for each mobile network operator. Population estimates were mapped into the locations of buildings and tents after excluding destroyed or severely damaged buildings. Counts of undamaged housing units and tents were based on UNOSAT's building damage estimates from 11 October 2025 and tent mapping product from 11 January 2026. Populations were estimated for grid cells outside the coverage area of both telecommunications providers by estimating the average number of people per housing unit/tent (~6 people) by integrating telecoms, building damage, and tent mapping data and applying that value to the map of tents and undamaged housing units outside tower coverage areas. Populations were assumed to be zero for grid cells with active evacuation orders and for areas behind the "yellow line" militarised area along the Gaza border. Because evacuation zones may have small populations remaining, we report those populations as "<100" or "<500" (less than 100 or less than 500 people). This methodology cannot produce quantitative measures of accuracy at any spatial scale due to lack of ground-truth validation data, so triangulation with multiple data sources is encouraged.</em> Source code for the analysis is available-upon-request from <a href="https://github.com/realgoodresearch/GazaNowPop" target="_blank">https://github.com/realgoodresearch/GazaNowPop</a> for authorised personnel.</p>


\newpage
# Population estimation for 25 Jan 2026
<!--
```{r}
#| echo: false
#| label: fig-pop-grid
#| fig-cap: "Population estimates for every 100-m grid cell."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_grid_", pop_date, ".jpg")
))
```
-->

```{r}
#| echo: false
#| label: fig-pop-nbr
#| fig-cap: "Population estimates aggregated to neighborhoods."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_nbr_", pop_date, ".jpg")
))
```


\newpage
## Governorate-level
```{r}
#| echo: false
#| results: asis

pop_gov_table <- pop_gov |>
  arrange(ADM2_PCODE) |>
  select(ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Population = population
  ) |>
  mutate(
    Population = case_when(
      Population > 500 ~ prettyNum(round(Population), big.mark = ","),
      Population >= 100 & Population < 500 ~ "<500",
      Population < 100 ~ "<100"
    )
  )

pop_gov_caption <- paste0(
  "Population estimates for each governorate on ",
  format(pop_date, "%d %B %Y")
)

pop_gov_table |>
  datatable(
    rownames = FALSE,
    caption = pop_gov_caption,
    options = list(
      paging = FALSE,
      searching = FALSE,
      scrollX = FALSE,
      scrollY = FALSE,
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )

```



## Municipality-level
```{r}
#| echo: false
#| results: asis

pop_mun_table <- pop_mun |>
  arrange(ADM2_PCODE, ADM3_PCODE) |>
  select(ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Population = population
  ) |>
  mutate(
    Population = case_when(
      Population > 500 ~ prettyNum(round(Population), big.mark = ","),
      Population >= 100 & Population < 500 ~ "<500",
      Population < 100 ~ "<100"
    )
  )

pop_mun_caption <- paste0(
  "Population estimates for each municipality on ",
  format(pop_date, "%d %B %Y")
)

pop_mun_table |>
  datatable(
    rownames = FALSE,
    caption = pop_mun_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )

```

## Neighbourhood-level
```{r}
#| echo: false
#| results: asis

pop_nbr_table <- pop_nbr |>
  arrange(ADM2_PCODE, ADM3_PCODE, ADM4_PCODE) |>
  select(ADM4_EN, ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Neighbourhood = ADM4_EN,
    Population = population
  ) |>
  mutate(
    Population = case_when(
      Population > 500 ~ prettyNum(round(Population), big.mark = ","),
      Population >= 100 & Population < 500 ~ "<500",
      Population < 100 ~ "<100"
    ),
    Municipality = case_when(
      nchar(Municipality) > 12 ~ paste0(substr(Municipality, 1, 12), "..."),
      TRUE ~ Municipality
    )
  )

pop_nbr_caption <- paste0(
  "Population estimates for each neighbourhood on ",
  format(pop_date, "%d %B %Y")
)

pop_nbr_table |>
  datatable(
    rownames = FALSE,
    caption = pop_nbr_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )

```

# Population change (16 Dec 2025 to 25 Jan 2026)
```{r}
#| echo: false
#| label: fig-pop-change-weekly
#| fig-cap: "Change in population for every neighbourhood from 16 December 2025 to 25 January 2026."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_change_", lastweek_date, "_to_", pop_date, ".jpg")
))
```

## Governorate-level
```{r}
#| echo: false
#| results: asis

pop_change_weekly_gov_table <- pop_change_weekly_gov |>
  arrange(ADM2_PCODE) |>
  select(ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Population_Change = population
  ) |>
  mutate(
    Population_Change = prettyNum(round(Population_Change), big.mark = ",")
  )

pop_change_weekly_gov_caption = paste0(
  "Estimates of population change for each governorate on ",
  format(pop_date, "%d %B %Y"),
  " compared to ",
  format(lastweek_date, "%d %B %Y")
)

pop_change_weekly_gov_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_weekly_gov_caption,
    options = list(
      searching = FALSE,
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = FALSE,
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```

## Municipality-level
```{r}
#| echo: false
#| results: asis

pop_change_weekly_mun_table <- pop_change_weekly_mun |>
  arrange(ADM2_PCODE, ADM3_PCODE) |>
  select(ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Population_Change = population
  ) |>
  mutate(
    Population_Change = prettyNum(round(Population_Change), big.mark = ",")
  )

pop_change_weekly_mun_caption = paste0(
  "Estimates of population change for each municipality on ",
  format(pop_date, "%d %B %Y"),
  " compared to ",
  format(lastweek_date, "%d %B %Y")
)

pop_change_weekly_mun_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_weekly_mun_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```

## Neighbourhood-level
```{r}
#| echo: false
#| results: asis
pop_change_weekly_nbr_table <- pop_change_weekly_nbr |>
  arrange(ADM2_PCODE, ADM3_PCODE, ADM4_PCODE) |>
  select(ADM4_EN, ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Neighbourhood = ADM4_EN,
    Pop_Change = population
  ) |>
  mutate(
    Pop_Change = prettyNum(round(Pop_Change), big.mark = ","),
    Municipality = case_when(
      nchar(Municipality) > 12 ~ paste0(substr(Municipality, 1, 12), "..."),
      TRUE ~ Municipality
    )
  )

pop_change_weekly_nbr_caption = paste0(
  "Estimates of population change for each neighbourhood on ",
  format(pop_date, "%d %B %Y"),
  " compared to ",
  format(lastweek_date, "%d %B %Y")
)

pop_change_weekly_nbr_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_weekly_nbr_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )

```

# Population change (29 Sept 2025 to 25 Jan 2026)
```{r}
#| echo: false
#| label: fig-pop-change-baseline
#| fig-cap: "Change in population for every neighbourhood from 29 September 2025 to 25 January 2026."
#| fig-width: 6
#| out.width: "70%"
#| fig-align: center
knitr::include_graphics(file.path(
  data_dir,
  paste0("fig_pop_change_", baseline_date, "_to_", pop_date, ".jpg")
))
```


## Governorate-level
```{r}
#| echo: false
#| results: asis

pop_change_gov_table <- pop_change_gov |>
  arrange(ADM2_PCODE) |>
  select(ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Population_Change = population
  ) |>
  mutate(
    Population_Change = prettyNum(round(Population_Change), big.mark = ",")
  )

pop_change_gov_caption = paste0(
  "Estimates of population change for each governorate on ",
  format(pop_date, "%d %B %Y"),
  "compared to",
  format(baseline_date, "%d %B %Y")
)

pop_change_gov_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_gov_caption,
    options = list(
      searching = FALSE,
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = FALSE,
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```

## Municipality-level
```{r}
#| echo: false
#| results: asis

pop_change_mun_table <- pop_change_mun |>
  arrange(ADM2_PCODE, ADM3_PCODE) |>
  select(ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Population_Change = population
  ) |>
  mutate(
    Population_Change = prettyNum(round(Population_Change), big.mark = ",")
  )

pop_change_mun_caption = paste0(
  "Estimates of population change for each municipality on ",
  format(pop_date, "%d %B %Y"),
  "compared to ",
  format(baseline_date, "%d %B %Y")
)

pop_change_mun_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_mun_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```

## Neighbourhood-level
```{r}
#| echo: false
#| results: asis
pop_change_nbr_table <- pop_change_nbr |>
  arrange(ADM2_PCODE, ADM3_PCODE, ADM4_PCODE) |>
  select(ADM4_EN, ADM3_EN, ADM2_EN, population) |>
  rename(
    Governorate = ADM2_EN,
    Municipality = ADM3_EN,
    Neighbourhood = ADM4_EN,
    Pop_Change = population
  ) |>
  mutate(
    Pop_Change = prettyNum(round(Pop_Change), big.mark = ","),
    Municipality = case_when(
      nchar(Municipality) > 12 ~ paste0(substr(Municipality, 1, 12), "..."),
      TRUE ~ Municipality
    )
  )

pop_change_nbr_caption = paste0(
  "Estimates of population change for each neighbourhood on ",
  format(pop_date, "%d %B %Y"),
  " compared to ",
  format(baseline_date, "%d %B %Y")
)

pop_change_nbr_table |>
  datatable(
    rownames = FALSE,
    caption = pop_change_nbr_caption,
    options = list(
      paging = FALSE,
      # pageLength = 25,
      scrollX = FALSE,
      scrollY = "50vh",
      autoWidth = TRUE
    ),
    class = "stripe hover compact"
  )
```




# Supplementary Data

The following supplementary data accompany this report and are available upon request to UNOCHA through the Assessment and Information Management (AIM) Working Group:

<ol>
<br>
<li><span class="filename">pop_nbr_[date].csv</span>:  Neighbourhood-level population estimates in csv format.</li>  
<li><span class="filename">pop_mun_[date].csv</span>:  Municipality-level population estimates in csv format.</li>  
<li><span class="filename">pop_gov_[date].csv</span>:  Governorate-level population estimates in csv format.</li>  

<br>

<!--
<li><span class="filename">pop_grid_[date].tif</span>:  Gridded (100-m) population estimates in geotiff raster format.</li>  
 -->
<li><span class="filename">pop_nbr_[date].gpkg</span>:  Neighbourhood-level population estimates in geopackage format to include spatial geometries defining neighbourhood boundaries.</li>  
<li><span class="filename">pop_mun_[date].gpkg</span>:  Municipality-level population estimates in geopackage format to include spatial geometries defining municipality boundaries.</li>  
<li><span class="filename">pop_gov_[date].gpkg</span>:  Governorate-level population estimates in geopackage format to include spatial geometries defining governorate boundaries.</li>  

<br>
<li><span class="filename">./pop_change_[from-date]/README.txt</span>:  Definition of the dates used to calculate population change.</li>
<li><span class="filename">./pop_change_[from-date]/pop_change_nbr_[date].csv</span>:  Neighbourhood-level estimates of population change in csv format.</li>  
<li><span class="filename">./pop_change_[from-date]/pop_change_mun_[date].csv</span>:  Municipality-level estimates of population change in csv format.</li>  
<li><span class="filename">./pop_change_[from-date]/pop_change_gov_[date].csv</span>:  Governorate-level estimates of population change in csv format.</li>  

<!--
<li><span class="filename">./pop_change_[from-date]/pop_change_grid_[date].tif</span>:  Gridded (100-m) estimates of population change in geotiff raster format.</li>  
 -->
<li><span class="filename">./pop_change_[from-date]/pop_change_nbr_[date].gpkg</span>:  Neighbourhood-level estimates of population change in geopackage format to include spatial geometries defining neighbourhood boundaries.</li>  
<li><span class="filename">./pop_change_[from-date]/pop_change_mun_[date].gpkg</span>:  Municipality-level estimates of population change in geopackage format to include spatial geometries defining municipality boundaries.</li>  
<li><span class="filename">./pop_change_[from-date]/pop_change_gov_[date].gpkg</span>:  Governorate-level estimates of population change in geopackage format to include spatial geometries defining governorate boundaries.</li>  

<br>
<!--
<li><span class="filename">fig_pop_grid_[date].jpg</span>:  A map of gridded population estimates (@fig-pop-grid) in JPEG format.</li>  
 -->
<li><span class="filename">fig_pop_nbr_[date].jpg</span>:  A map of neighborhood-level population estimates (@fig-pop-nbr) in JPEG format.</li>  
<li><span class="filename">fig_pop_nbr_change_[date]_to__[date].jpg</span>:  A map of neighbourhood level estimates of population change (@fig-pop-change-weekly, @fig-pop-change-baseline) in JPEG format.</li>  
<ol>
